Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-07-15 tse19/main.tex
updates RQ7

To answer this research question, we selected 15 different subjects,
ran their test suites against all configurations described in
Section~\ref{sec:modes}, and compared their running times and rate of
test flakiness.  We used the sequential execution configuration,
\emph{\Seq{}}, as the comparison baseline in this experiment.  To
select subjects, we sorted projects whose test suites run in 1m or
more by decreasing order of execution time and selected the first
fifteen projects that use JUnit 4.7 or later.  The rationale for this
criteria is to ensure compatibility with parallel configuration since
older versions of JUnit does not support parallel testing.  We ran
each project on each configuration for \SubjectsReruns{} times.
Overall, we needed to reran test suites 270 times, 18 times (3x6
configurations) on each project.  Given the low standard deviations
observed in our measurements\Comment{ and the aggregated time cost of 270 test
executions}, we considered \SubjectsReruns{} reruns reasonable for this
experiment.

@@

We used Maven log files to identify test classes to run and used the
Maven dependency plugin~\cite{maven-dep} to build the project's
classpath (with the command \CodeIn{mvn dependency:build-classpath}).
Once we find the tests suite to run and the corresponding classpath,
we invoke the test runners mentioned above on them.  We configured
this experiment to run at most three JVMs in parallel.  Recall that in
our setup (see Section~\ref{sec:setup}), we limited our kernel to use
only three cores and reserved one core for OS-related processes.  To
ensure that our experiments terminate (recall that deadlock or
livelock could occur) we used the \CodeIn{timeout}
command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
if test execution exceeds a given time limit. Finally, we save each
execution log and stack traces generated from JUnit to collect the
execution time, the number of failing tests, and to diagnose outliers
in our results.

\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
subject's name.  Values are averaged across multiple executions.  We
did not report standard deviations as they are very small in all
cases.  As to identify the potential causes of flakiness, we inspected
the exceptions reported in execution logs. We found that, in most
of the cases, flakiness was caused by race conditions: approximately
97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
caused by concurrent access on unsynchronized data structures.\Comment{
  More precisely, the manifested exceptions were
  \CodeInF{ConcurrentModificationException} (0.8\%),
  \CodeInF{NoSuchElementException} (0.7\%), and
  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
broken test dependencies were not as prevalent as race conditions
(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
anticipating race conditions to schedule test executions would have
higher impact compared to breaking test dependencies using a tool such
as ElectricTest~\cite{bell-etal-esecfse2015}.

The projects with flakiness
in all configurations were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and
\CodeIn{Moquette}.  It is worth highlighting the unfortunate case of
\CodeIn{Moquette}, which manifested more than 20\% flaky tests in
every configuration.  Considering time, it is noticeable from the
averages, perhaps as expected, an increasing speedup from
configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.  Overall, results show that
0\% of flakiness have been reported in 30 of the 75 (=5x15)
pairs of project and configuration we analyzed (40\% of the total).
In for 4 of the 15 projects flakiness was not manifested in 
any combination pairs.  We noticed with some surprise that the average speedup of
configuration \emph{\SeqClassParMeth} was higher compared to
\emph{\ForkParMeth} indicating that it is not always the case that
using more CPUs pays off. Important to note that the cost of spawning
new JVMs can be significant in \emph{\ForkParMeth}.

\begin{mdframed}
\noindent\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 73.33\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{mdframed}

>>>>

To answer this research question, we selected 21 different subjects,
ran their test suites against all configurations described in
Section~\ref{sec:modes}, and compared their running times and rate of
test flakiness.  We used the sequential execution configuration,
\emph{\Seq{}}, as the comparison baseline in this experiment.  To
select subjects, we sorted projects whose test suites run in 5m or
more by decreasing order of execution time and selected the first
twenty one projects that use JUnit 4.7 or later.  The rationale for this
criteria is to ensure compatibility with parallel configuration since
older versions of JUnit does not support parallel testing.  We ran
each project on each configuration for twelve times.
Overall, we needed to reran test suites 1,512 times, 72 times (12x6
configurations) on each project.  Given the low standard deviations
observed in our measurements\Comment{ and the aggregated time cost of 270 test
executions}, we considered twelve reruns reasonable for this
experiment.

@@

We used Maven log files to identify test classes to run and used the
Maven dependency plugin~\cite{maven-dep} to build the project's
classpath (with the command \CodeIn{mvn dependency:build-classpath}).
Once we find the tests suite to run and the corresponding classpath,
we invoke the test runners mentioned above on them.  We configured
this experiment to run at most twelve JVMs in parallel.  Recall that in
our setup (see Section~\ref{sec:setup}), we limited our kernel to use
only three cores and reserved one core for OS-related processes.  To
ensure that our experiments terminate (recall that deadlock or
livelock could occur) we used the \CodeIn{timeout}
command~\cite{timeout-cmd} configured to dispatch a \emph{kill} signal
if test execution exceeds a given time limit. Finally, we save each
execution log and stack traces generated from JUnit to collect the
execution time, the number of failing tests, and to diagnose outliers
in our results.

\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
subject's name.  Values are averaged across multiple executions.  We
did not report standard deviations as they are very small in all
cases.  As to identify the potential causes of flakiness, we inspected
the exceptions reported in execution logs. We found that, in most
of the cases, flakiness was caused by race conditions: approximately
95.8\% of the failures were caused by a \CodeInF{null} dereference and 2.7\% were
caused by concurrent access on unsynchronized data structures. Cases of likely
broken test dependencies were not as prevalent as race conditions
(1.5\% of the total): \CodeInF{EOFException} (0.2\%),
\CodeInF{FileSystemAlreadyExistsException} (0.5\%), and
\CodeInF{BufferOverflowException} (0.8\%). Results suggest that
anticipating race conditions to schedule test executions would have
higher impact compared to breaking test dependencies using a tool such
as ElectricTest~\cite{bell-etal-esecfse2015}.

The projects with flakiness
in all configurations were \CodeIn{Activity}, \CodeIn{Incubator Dubbo}, \CodeIn{DROID}, and
\CodeIn{Hawkbit}.  It is worth highlighting the unfortunate case of
\CodeIn{Hawkbit}, which manifested more than 9\% flaky tests in
every configuration.  Considering time, it is noticeable from the
averages, perhaps as expected, an increasing speedup from
configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.  Overall, results show that
0\% of flakiness have been reported in 47 of the 105 (=5x15)
pairs of project and configuration we analyzed (44.76\% of the total).
In for 6 of the 21 projects flakiness was not manifested in 
any combination pairs.  We noticed with some surprise that the average speedup of
configuration \emph{\SeqClassParMeth} was higher compared to \emph{\ParClassSeqMeth}{C2} and \emph{\ParClassParMeth}{C3},
indicating that it is not always the case that
using more CPUs pays off. Important to note that the cost of spawning
new JVMs can be significant in \emph{\ForkParMeth}.

\begin{mdframed}
\noindent\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 44.76\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{mdframed}
